The Supervisionary proof-checking kernel

### 2021-10-26 paper/prisc-2022.tex
prisc-2022: start bibliography

@@

Interactive theorem proving software is typically designed around a trusted proof-checking \deffont{kernel}, the sole system component capable of authenticating theorems.
Untrusted automation procedures reside outside of the kernel, and drives it to deduce new theorems via an API.
Kernel and untrusted automation are typically implemented in the same programming language---the ``meta-language''---usually some functional programming language in the ML family.
This strategy---introduced by Milner in his LCF proof assistant---is a reliability mechanism, aiming to ensure that any purported theorem produced by the system is indeed a legitimate entailment from the theory within the logic.

@@

\emph{Supervisionary} is a proof-checking system for Gordon's HOL, structured as supervisory software, and provides a \deffont{system interface} to untrusted code similar to an operating system's system call interface.
Supervisionary is implemented as a WebAssembly (Wasm henceforth) host, allowing us to prototype rapidly.

@@

Given our use of Wasm, we could extend our system interface by also implementing the Wasm System Interface---a POSIX-like interface for Wasm.
This would transform Supervisionary from a mere programmable proof-checker into a general-purpose sandbox, capable of executing arbitrary programs, albeit with an unusual interface for constructing proofs.

@@

>>>>

\acmConference[PriSC'22]{6th Workshop on Principles of Secure Compilation}{January 22, 2022}{Philadelphia, PA, USA}
\acmYear{2022}
\acmISBN{}
\acmDOI{}

@@

Interactive theorem proving software is typically designed around a trusted proof-checking \deffont{kernel}, the sole system component capable of authenticating theorems.
Untrusted automation procedures reside outside of the kernel, and drives it to deduce new theorems via an API.
Kernel and untrusted automation are typically implemented in the same programming language---the ``meta-language''---usually some functional programming language in the ML family.
This strategy---introduced by Milner in his LCF proof assistant~\cite{Milner1972LogicFC}---is a reliability mechanism, aiming to ensure that any purported theorem produced by the system is indeed a legitimate entailment from the theory within the logic.

@@

\emph{Supervisionary} is a proof-checking system for Gordon's HOL, structured as supervisory software, and provides a \deffont{system interface} to untrusted code similar to an operating system's system call interface.
Supervisionary is implemented as a WebAssembly~\cite{DBLP:conf/pldi/HaasRSTHGWZB17} (Wasm henceforth) host, allowing us to prototype rapidly.

@@

Given our use of Wasm, we could extend our system interface by also implementing the Wasm System Interface~\cite{Wasi}---a POSIX-like interface for Wasm.
This would transform Supervisionary from a mere programmable proof-checker into a general-purpose sandbox, capable of executing arbitrary programs, albeit with an unusual interface for constructing proofs.

@@

\newpage

\bibliography{prisc-2022}
